Fifteen years of decentralization attempts

### 2014-03-20 paper.tex
Fixed typo
changed certs to certificates

		Tor currently uses an interactive forward-secret key-exchange protocol called the \emph{Tor Authentication Protocol} (TAP) \cite{backes2012ace}. This protocol uses telescoping, which means that the initiator negotiates session keys with each successive hop in the circuit. There are several proposals for more efficient key exchange methods. One of them is \emph{ACE}, a one-way authenticated key exchange protocol. The authors of this methods claim to have an 46\% efficiency improvement on the side of the client and nearly 19\% on the side of the Onion Routers. ACE requires clients to send one extra element in the key exchange. This does not introduce any overhead however, because the element fits in the unused space in a cell.

@@

		The Myrmic DHT runs on top of Kademlia, and introduces the Neighbourhood Authority. This authority issues certs to nodes that participate in the DHT, but it does not participate in the DHT itself. The NA makes this solution not a fully decentralized one, but its role is a lot smaller than the current Directory Servers. This does not solve the trust issue, but it does solve the scalability issue.

>>>>

		Tor currently uses an interactive forward-secret key-exchange protocol called the \emph{Tor Authentication Protocol} (TAP) \cite{backes2012ace}. This protocol uses telescoping, which means that the initiator negotiates session keys with each successive hop in the circuit. There are several proposals for more efficient key exchange methods. One of them is \emph{ACE}, an one-way authenticated key exchange protocol. The authors of this methods claim to have an 46\% efficiency improvement on the side of the client and nearly 19\% on the side of the Onion Routers. ACE requires clients to send one extra element in the key exchange. This does not introduce any overhead however, because the element fits in the unused space in a cell.

@@

		The Myrmic DHT runs on top of Kademlia, and introduces the Neighbourhood Authority. This authority issues certificates to nodes that participate in the DHT, but it does not participate in the DHT itself. The NA makes this solution not a fully decentralized one, but its role is a lot smaller than the current Directory Servers. This does not solve the trust issue, but it does solve the scalability issue.
